%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

\namesection{}{Md Sirajus Salayhin}{ 
\urlstyle{same}\url{http://salayhin.wordpress.com} \\
\href{mailto:salayhin@gmail.com}{salayhin@gmail.com} | +880+-1833362458}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IICT, BUET}
\descript{Post Graduate Diploma in ICT}
\location{Expected Sep 2018| Dhaka, Bangladesh}
\sectionsep

\subsection{Jagannath University}
\descript{B.Sc in Physics}
\location{2008 | Dhaka, Bangladesh}
\sectionsep

\subsection{New Govt. Degree College}
\descript{H.S.C}
\location{2003 | Rajshahi, Bangladesh}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Profiles} 
Github:// \href{https://github.com/salayhin}{\custombold{salayhin}} \\
LinkedIn://  \href{https://www.linkedin.com/in/salayhin}{\custombold{salayhin}} \\
StackOverflow://  \href{https://stackoverflow.com/users/717600/sirajus-salayhin}{\custombold{salayhin}} \\
Twitter://  \href{https://twitter.com/salayhin}{\custombold{@salayhin}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\textbullet{} Python \textbullet{} R \textbullet{} Ruby \textbullet{} Shell \textbullet{} SQL \\

\subsection{}
\subsection{Database}
\textbullet{} SQL Server 2016 \textbullet{} MySQL \textbullet{} PostgraSQL \\

\subsection{}
\subsection{Web Scraping Tools}
\textbullet{} Scrapy \textbullet{} Beautiful Soup \\

\subsection{}
\subsection{Data Analysis Tools}
\textbf{Python:} Jupyter Notebook \textbullet{} Numpy \textbullet{} Pandas \textbullet{} matplotlib\\
\subsection{}
\textbf{R:} dplyr \textbullet{} ggplot \textbullet{} RShiny \\ 

\subsection{}
\subsection{Machine Learning Tools}
\textbf{Python:} Scikit-learn \textbullet{} Tensorflow \\
\subsection{}
\textbf{R:} caret \\

\subsection{}
\subsection{Deployment}
\textbullet{} AWS \textbullet{} Google Cloud \textbullet{} Cent OS  \textbullet{} Ubuntu \textbullet{} Docker \\

\subsection{}
\subsection{Web}
\textbullet{} Ruby on Rails \textbullet{} Django \textbullet{} Flask


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Pathao Ltd.}
\descript{| Senior Data Engineer }
\location{May 2018 – Now | Dhaka, Bangladesh}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed, modeled and implemented Data Warehouse and Data Mart using Google Cloud Platform like Dataflow, Cloud SQL and Big Query 
\end{tightemize}
\sectionsep

\runsubsection{Augmedix INC.}
\descript{| Senior Data Engineer }
\location{June 2015 – March 2018 | Dhaka, Bangladesh}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed, modeled and implemented Data Warehouse and Data Mart (SQL Server 2016)
\item Developed ETL for import data from various sources like 3rd Party API's, Google Spreadsheet, MySQL (R, Python and Pentaho)
\item Integrate Apache Airflow for data pipeline workflow scheduling and monitoring.
\item Manage and Deploy ETL application developed with Python, R and Pentaho in AWS servers.
\item Develop AWS EC2 and RDS monitoring tool using RShiny.
\item Develop automated testing script for ETL using R and RShiny.
\item Created REST API for expose data (Python, Django REST API).
\item Tools: R, Python, Pandas, dplyr, NumPy, Matplotlib, Jupyter Notebook, Django, RShiny
\end{tightemize}
\sectionsep

\runsubsection{Nascenia Ltd.}
\descript{| Ruby on Rails Developer }
\location{June 2013 – June 2015 | Dhaka, Bangladesh}
\begin{tightemize}
\item Developed Web Application using Ruby on Rails. For example: On-line Marketplace, Social media data analysis tool, School Management System Software
\item Manage and deploy RoR applications in AWS EC2.
\item Tools: Ruby on Rails, PostgreSQL, MySQL, Apache Solr
\end{tightemize}
\sectionsep

\runsubsection{Right Brain Solution}
\descript{| Software Engineer}
\location{Nov 2011 – May 2013 | Dhaka, Bangladesh}
\begin{tightemize}
\item Developed Web application API for iphone and android apps.
\item Tools: Zend Framework, Symfony 2, MySQL, MongoDB
\end{tightemize}
\sectionsep

\runsubsection{Nanosoft}
\descript{| Programmer}
\location{May 2011 – Oct 2011 | Dhaka, Bangladesh}
\begin{tightemize}
\item Created web based application for schedule management system for 
\item Tools: Codeigniter, MySQL
\end{tightemize}
\sectionsep

\runsubsection{Sitebloom Ltd.}
\descript{| Software Developer}
\location{Oct 2009 – Jun 2011 | Dhaka, Bangladesh}
\begin{tightemize}
\item Created web based school management system software (Codeigniter, MySQL)
\item Tools: Codeigniter, MySQL
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certification}
\href{https://www.coursera.org/account/accomplishments/certificate/PB48PJLRP5VQ}{\custombold{Coursera: Introduction to Data Science in Python }} \\
\href{https://www.datacamp.com/courses/python-data-science-toolbox-part-1}{\custombold{Datacamp: Python Data Science Toolbox (Part 1) }} \\
\href{https://www.datacamp.com/courses/python-data-science-toolbox-part-2}{\custombold{Datacamp: Python Data Science Toolbox (Part 2) }} \\
\href{https://www.datacamp.com/courses/exploratory-data-analysis}{\custombold{Datacamp: Exploratory Data Analysis Using R
 }} \\
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
